以太坊：一种安全去中心化的通用交易账本 \\ {\smaller \textbf{EIP-150版本 (\YellowPaperVersionNumber{})}}

### 2017-08-23 Paper_Chinese.tex
update

It is assumed that the client will have stored the pair $(\mathtt{\tiny KEC}(I_\mathbf{b}), I_\mathbf{b})$ at some point prior in order to make the determination of $I_\mathbf{b}$ feasible.

As can be seen, there are four exceptions to the usage of the general execution framework $\Xi$ for evaluation of the message call: these are four so-called `precompiled' contracts, meant as a preliminary piece of architecture that may later become \textit{native extensions}. The four contracts in addresses 1, 2, 3 and 4 execute the elliptic curve public key recovery function, the SHA2 256-bit hash scheme, the RIPEMD 160-bit hash scheme and the identity function respectively.

Their full formal definition is in Appendix \ref{app:precompiled}.

\section{Execution Model} \label{ch:model}

@@

\subsection{Basics}

@@

\subsection{Fees Overview}

>>>>

我们假设客户端会先保存数据对 $(\mathtt{\tiny KEC}(I_\mathbf{b}), I_\mathbf{b})$ , 以便更方便地根据 $I_\mathbf{b}$ 做出决定。

如我们所见，消息调用执行框架 $\Xi$ 中有4个特例: 这四个是‘预编译’合约，作为最初架构中的一部分后续可能会变成本地扩展。这四个合约地址分别为1、2、3和4，分别是用来执行椭圆曲线公钥恢复函数、SHA2 256位哈希方案、RIPEMD 160位哈希方案和身份函数。

这4个合约的详细定义见附录 \ref{app:precompiled}。

\section{执行模型} \label{ch:model}

@@

\subsection{基础}

@@

\subsection{费用概览}
